Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-06-26 Paper/main.tex

\begin{figure}[H]
    \caption{Differences in claims and compensation by case file outcome}
    \label{claimsvsoutcomes}
    \begin{center}
        \includegraphics[width=0.7\textwidth]{Amountasked.tiff}
        \end{center}
    \footnotesize \textit{Notes: This graph shows the average amount (in thousand pesos) asked, won, minimum legal compensation, and minimum legal compensation plus lost wages, by outcome. The bottom legend shows the percentage of cases with each outcome for our database (N=5005). Note that, by definition, workers have no chance of recovery in drops and expiries. In our data, all settlements imply a positive recovery for the worker; finally, \textbf{for judgments, only 24\% of the time does the worker recover anything.}} 
    {\footnotesize \textit{Script: } \texttt{amount\_plots.R}}
\end{figure}

>>>>

\begin{figure}[H]
    \caption{Differences in claims and compensation by case file outcome}
    \label{claimsvsoutcomes}
    \begin{center}
        \includegraphics[width=0.7\textwidth]{Amountasked.tiff}
        \end{center}
    \footnotesize \textit{Notes: This graph shows the average amount (in thousand pesos) asked, won (overall and conditional on winning), minimum legal compensation, and minimum legal compensation plus lost wages, by outcome. The bottom legend shows the percentage of cases with each outcome for our database (N=5005). Note that, by definition, workers have no chance of recovery in drops and expiries. In our data, all settlements imply a positive recovery for the worker; finally, \textbf{for judgments, only 24\% of the time does the worker recover anything.}} 
    {\footnotesize \textit{Script: } \texttt{amount\_plots.R}}
\end{figure}
